A Few Easy Pieces: \\ How to enhance your relationship with your future self.

### 2011-03-17 workflow.Rnw
Editing the document

\author{Jake Bowers\thanks{Many thanks to Mark Fredrickson, Brian
    Gaines, Kieran Healy, Kevin Quinn and Cara Wong for direct help on
    this document, Mika LaVaque-Manty, Ben Hansen, and Mark
    Fredrickson for many useful discussions on this topic. The source
    code for this document may be freely downloaded from
    \url{https://github.com/jwbowers/workflow}.}}

@@

\usepackage[noae,nogin]{Sweave} %Declaring this explicitly so that I can modify the Sweave environment here rather in Sweave.sty which will be c
\DefineVerbatimEnvironment{Sinput}{Verbatim} {xleftmargin=.5em,fontsize=\footnotesize}
\DefineVerbatimEnvironment{Soutput}{Verbatim}{xleftmargin=.5em,fontsize=\footnotesize}
\DefineVerbatimEnvironment{Scode}{Verbatim}{xleftmargin=.5em,fontsize=\footnotesize}
\fvset{listparameters={\setlength{\topsep}{0pt}}}
\renewenvironment{Schunk}{\vspace{\topsep}}{\vspace{\topsep}}
\SweaveOpts{keep.source=TRUE}  %Show comments
\fvset{fontsize=\normalsize} %slightly smaller verbatim font

@@

<<initialize,echo=FALSE,results=hide>>=
  ##First, just setup the \R environment:

  options(SweaveHooks=list(
            fig=function(){
              par(mar=c(3.5, 3, 1.1, 0),
                  pty="s",
                  mgp=c(1.5,0.5,0),
                  oma=c(0,0,0,0))},#,
            echo=function(){options(continue=" ") ##Don't show "+" prompts,
                            options(prompt=" ")}
            ),
          digits=3,
          scipen=8,
          width=100,
          error=function(){options(prompt="> ",continue="+ ");NULL}
          )

@@

An idea is born in a coffee shop, a seminar, a quiet walk. It is a
cold winter in 2011, but the idea energizes the student. The idea is
why he went to graduate school.

This idea inspires a seminar paper in the spring. And a conference
paper arises from the seminar paper in collaboration with another
student in 2012. A dissertation chapter descends from the conference
paper in 2013. Other dissertation chapters take up 2014. A submission
to a journal with the original co-author and a new collaborator
happens in 2015. Revision and resubmission wait until 2017 while
harried editors, reviewers and authors strive to balance teaching,
service, and life. The three collaborators have luckily found work in
three different universities around the world. In 2018 a child is born
and a paper is published. In 2020 a graduate student in a coffee shop
reads the paper and has an idea that challenges the analysis in the
paper. What would happen if only the first author had thought to
control for X? Or run one more MCMC chain? Or chosen a different
likelihood function? Will the United Nations (now eager to act based
                                              the paper) make a wrong move?

The first author convenes a three way video conference with the other
collaborators while commuting home in his flying car. The group must
go back to the analyses. Which ones? The ones from 2011? Or 2012? Or
2018? Where are the files? The next day, one member of the group finds
some of the files. Now the checks and re-analyses should be
easy. Right? The student, now professor, is the same person and
should remember the reason for those bits of code (or at least should
                                                   remember which series of mouse clicks were used to produce the numbers
                                                   for that crucial table --- and those mouse clicks should not be time
                                                   consuming to redo exactly as they were done in 2011, or was it
                                                   2015?). And, of course, the way Microsoft Word/Stata/SPSS/R/LISREL
stores files and the way that your machine reads and writes them is
the same, right --- since Windows and Mac OS X have always existed and
will always continue to exist more or less as they currently exist? And
the group knows exactly which bit of code produced which table and
which figure, right? And they wrote their code following Nagler's
Maxims \citep{nagler1995coding} and  King's Replication
Standard \citep{king1995replication} right?

>>>>

\author{Jake Bowers\thanks{I owe many thanks to Mark Fredrickson,
    Brian Gaines, Mark Fredrickson, Kieran Healy, Kevin Quinn and Cara
    Wong for direct help on this document and to Mika LaVaque-Manty
    and Ben Hansen for many useful discussions on this topic. The
    source code for this document may be freely downloaded and
    modified from \url{https://github.com/jwbowers/workflow}.}}

@@

\usepackage[noae,nogin]{Sweave} %Declaring this explicitly so that I can modify the Sweave environment here rather in Sweave.sty which will be c
\DefineVerbatimEnvironment{Sinput}{Verbatim} {xleftmargin=.5em,fontsize=\small}
\DefineVerbatimEnvironment{Soutput}{Verbatim}{xleftmargin=.5em,fontsize=\small}
\DefineVerbatimEnvironment{Scode}{Verbatim}  {xleftmargin=.5em,fontsize=\small}
\fvset{listparameters={\setlength{\topsep}{0pt}}}
\renewenvironment{Schunk}{\vspace{\topsep}}{\vspace{\topsep}}
\SweaveOpts{keep.source=TRUE}  %Show comments
\fvset{fontsize=\small} %slightly smaller verbatim font

@@

<<initialize,echo=FALSE,results=hide>>=
  ##First, just setup the \R environment:
  options(SweaveHooks=list(
            fig=function(){
              par(mar=c(3.5, 3, 1.1, 0),
                  pty="s",
                  mgp=c(1.5,0.5,0),
                  oma=c(0,0,0,0))},#,
            echo=function(){options(continue=" ") ##Don't show "+" prompts,
                            options(prompt=" ")}
            ),
          digits=3,
          scipen=8,
          width=100,
          error=function(){options(prompt="> ",continue="+ ");NULL}
          )

@@

An idea is born in a coffee shop, a seminar, a quiet walk. It is a
gray winter in 2011, but the idea dispells February's doldrums and
energizes the student.% Now he knows why he went to graduate school.

This idea inspires a seminar paper in the spring. And a conference
paper arises from the seminar paper in collaboration with another
student in 2012. A dissertation chapter descends from the conference
paper in 2013. Other dissertation chapters take up 2014. A submission
to a journal with the original co-author and a new collaborator
happens in 2015. Revision and resubmission wait until 2017 while
harried editors, reviewers and authors strive to balance teaching,
service, and life. By now, the three lucky collaborators work as
professors in three different universities. In 2018 a child is born
and a paper is published. The United Nations takes an interest in the
paper in 2019 and hosts a conference to discuss implications of the
research. In 2020 a first year graduate student in a coffee shop has
an idea that challenges the analysis in the now famous paper. What
would happen if they had controlled for X? Or run one more MCMC chain?
Or chosen a different likelihood function?  Will the United Nations
(now eager to act based the paper) make a wrong move?

The first author convenes a three way video conference with the other
collaborators during his homeward commute while his flying car is in
auto-drive mode (video chatting during manual driving having been
outlawed in his state in 2017). The group must go back to the
analyses. Which ones?  The ones from 2011? Or 2012? Or 2018? Where are
the files? The next day, one member of the group who has kept some
hard-drives around out of nostalgia (the same guy who still owns
cassette tapes) finds some of the files. Now the checks and
re-analyses should be easy. Right? The student, now professor, is the
same person and should remember the reason for those bits of code (or
at least should remember which series of mouse clicks were used to
produce the numbers for that crucial table --- and those mouse clicks
should not be time consuming to redo exactly as they were done in
2011, or was it 2015?). Right? And, of course, the way Microsoft
Word/Stata/SPSS/R/LISREL stores files and the way that current machines in 2020
read and write them is the same --- since Windows and Mac OS
X have always existed and will always continue to exist more or less
as they currently exist? Right? And the group knows exactly which bit of code
produced which table and which figure, right? And they wrote their
code following Nagler's Maxims \citep{nagler1995coding} and King's
Replication Standard \citep{king1995replication} right?

Right? Wrong? If the collaborators find themselves answering ``wrong'' to many of those questions

If the original analyses were not done via typing in commands in plain
text files, these authors will be in a pickle in 2020.
